Accurate Measurement of Bicycle Parameters

### 2010-10-19 papers/BMD2010/PhysicalParametersPoster/poster.tex
poster final draft again and I'm sitting in 't klooster in delft drinking fine beer and eating fine cheese

  \begin{alertblock}{Bicycle Eigenanalysis}
    \rmfamily{
    Distinct variation is apparent among the bicycles' eigenvalues. Frequency,
    damping, and the stable speed range can be compared to the physical
    differences of the bicycles. The bicycles also exhibit a two imaginary root
    pairs at low speeds.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/Bike/eig_plot.pdf}
    \end{center}
    \rmfamily{
    Less variation is seen among the bicycles when a
    rigid rider is added, except in the stable sppeed ranges.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/BikeRider/eig_plot.pdf}
    \end{center}
  \end{alertblock}

@@

% The fourth column
\begin{column}{\onecolwid}
        \begin{block}{Measurements}
            \rmfamily{
            We estimated the wheel radii by measuring the distance traveled
            by the loaded wheels, the trail by directly measuring the fork
            offset and the wheelbase and headtube angle by direct measurement.
            We measured the mass of the four bodies (fork, frame, and
            wheels) directly using an precision scale. We found the location of
            the mass center by hanging the bodies in multiple orientations
            through their mass centers.
            }
            \\
            \begin{center}
              \includegraphics[width=0.8\onecolwid]{../../../figures/angles.pdf}
            \end{center}
            \rmfamily{
            The in- and out-of-symmetric plane moments of inertia were estimated by
            hanging the bodies as torsional and compound pendulums,
            respectively. We then estimated the period of oscillation by
            fitting a decaying osciallation function to a voltage signal from a
            rate gyro after the pendulums were perturbed. The period can then
            be correlated to the inertia.
            }
            \\
            \begin{center}
              \includegraphics[width=0.90\onecolwid]{../../../plots/PendFit/BrowserFrameCompoundFirst1.pdf}
            \end{center}
        \end{block}

@@

\begin{column}{\onecolwid}
  % Frequency Response
  \begin{alertblock}{Bicycle Frequency Response}
    \small{\rmfamily{
    The steer torque to roll angle Bode plot reveals up to 10 dB variation
    among the bikes and variation in phase.
    }}
    \\
    \begin{center}
      \includegraphics[width=.85\onecolwid]{../../../plots/Bike/Bode/Tdel2phi.pdf}
      \\
      \includegraphics[width=.85\onecolwid]{../../../plots/BikeRider/Bode/Tdel2phi.pdf}
    \end{center}
  \end{alertblock}

>>>>

  \begin{alertblock}{Eigenanalysis}
    \rmfamily{
    Distinct variation is apparent among the bicycles' eigenvalues. Frequency,
    damping, and the stable speed range can be compared to the physical
    differences of the bicycles. The bicycles also exhibit a two imaginary root
    pairs at low speeds.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/Bike/eig_plot.pdf}
    \end{center}
    \rmfamily{
    Less variation is seen among the bicycles when a
    rigid rider is added, except in the stable speed ranges.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/BikeRider/eig_plot.pdf}
    \end{center}
  \end{alertblock}

@@

% The fourth column
\begin{column}{\onecolwid}
        \begin{block}{Measurements}
            \rmfamily{
            We estimated the wheel radii by measuring the distance traveled
            by the loaded wheels, the trail by directly measuring the fork
            offset and the wheelbase and headtube angle by direct measurement.
            We measured the mass of the four bodies (fork, frame, and
            wheels) directly using an precision scale. We found the location of
            the mass center by hanging the bodies in multiple orientations
            through their mass centers.
            }
            \\
            \begin{center}
              \includegraphics[width=0.8\onecolwid]{../../../figures/angles.pdf}
            \end{center}
            \rmfamily{
            The in- and out-of-symmetric plane moments of inertia were estimated by
            hanging the bodies as torsional and compound pendulums,
            respectively. We then estimated the period of oscillation by
            fitting a decaying oscillation function to a voltage signal from a
            rate gyro after the pendulums were perturbed. The period can then
            be correlated to the inertia.
            }
            \\
            \begin{center}
              \includegraphics[width=0.90\onecolwid]{../../../plots/PendFit/BrowserFrameCompoundFirst1.pdf}
            \end{center}
        \end{block}

@@

\begin{column}{\onecolwid}
  % Frequency Response
  \begin{alertblock}{Frequency Response}
    \small{\rmfamily{
    The steer torque to roll angle Bode plot reveals up to 10 dB variation
    among the bikes and variation in phase.
    }}
    \\
    \begin{center}
      \includegraphics[width=.85\onecolwid]{../../../plots/Bike/Bode/Tdel2phi.pdf}
      \\
      \includegraphics[width=.85\onecolwid]{../../../plots/BikeRider/Bode/Tdel2phi.pdf}
    \end{center}
  \end{alertblock}
